Capabilities, MMIO and Robust Safety

### 2020-03-25 capability-meetings-notes/10-03/main.tex
MMIO meeting notes: fix: boot code must prove that the driver is distinct from the adversary
MMIO writeup: Instr Executable -> Seq (Instr Executable)
Fix a typo

\[
  \begin{array}{l}
  \X{bootSpec}(P, g, b, e, A_{\X{entry}}) \eqdef {} \\[0.8em]
    \quad
  \begin{array}{l}
    \left\{
    \begin{array}{l}
      \X{PC} \mapsto_{r} (\X{RWX}, \X{G}, 0, \X{MEM_{MAX}}, l_{\X{boot}}) \ast {} \\[0.5em]
      \bigast{r \in \X{Reg} \setminus \X{PC}}{r \mapsto_{r} \_}
      \ast \bigast{m \in \X{Mem} \setminus \MMIO}{m \mapsto_{a} \_}
      \ast \tracefrag{\emptyset}
    \end{array}
    \right\}
    \\[2em]
    \quad \I{Instr}\; \I{Executable}
    \\[0.5em]
    \left\{
    \begin{array}{l}
      \exists b_{adv}\; e_{adv}\; t.\; \\[0.5em]
      \quad
      \begin{array}{l}
        \X{PC} \mapsto_{r} (\X{RWX}, \X{G}, b_{adv}, e_{adv}, b_{adv}) \ast {} \\[0.7em]
        \bigast{a_{i} \in A_{\X{entry}}}{a_{i} \mapsto_{r} (\X{E},g,b,e,a_i)} \ast
        \bigast{r \in Reg\setminus \{\X{PC}, A_{\X{entry}}\}}{r \mapsto_{r} \X{inl}\; \_} \ast {} \\[1.4em]
        \bigast{m \in [b_{adv}, e_{adv})}{m \mapsto_{a} \X{inl}\; \_} \ast 
        \tracefrag{t} \ast \pure{P(t)}
      \end{array}
    \end{array}
    \right\}
  \end{array}
  \end{array}
\]

@@

The resulting boot-code-base formulation of the robust safety theorem is now a
corollary of the general robust safety theorem, and has the following statement:

>>>>

\[
  \begin{array}{l}
  \X{bootSpec}(P, g, b, e, A_{\X{entry}}) \eqdef {} \\[0.8em]
    \quad
  \begin{array}{l}
    \left\{
    \begin{array}{l}
      \X{PC} \mapsto_{r} (\X{RWX}, \X{G}, 0, \X{MEM_{MAX}}, l_{\X{boot}}) \ast {} \\[0.5em]
      \bigast{r \in \X{Reg} \setminus \X{PC}}{r \mapsto_{r} \_}
      \ast \bigast{m \in \X{Mem} \setminus \MMIO}{m \mapsto_{a} \_}
      \ast \; \tracefrag{\emptyset}
    \end{array}
    \right\}
    \\[2em]
    \quad \I{Seq}\; (\I{Instr}\; \I{Executable})
    \\[0.5em]
    \left\{
    \begin{array}{l}
      \exists b_{adv}\; e_{adv}\; t.\; \\[0.5em]
      \quad
      \begin{array}{l}
        \X{PC} \mapsto_{r} (\X{RWX}, \X{G}, b_{adv}, e_{adv}, b_{adv}) \ast {} \\[0.7em]
        \bigast{a_{i} \in A_{\X{entry}}}{a_{i} \mapsto_{r} (\X{E},g,b,e,a_i)} \ast
        \bigast{r \in Reg\setminus \{\X{PC}, A_{\X{entry}}\}}{r \mapsto_{r} \X{inl}\; \_} \ast {} \\[1.4em]
        \bigast{m \in [b_{adv}, e_{adv})}{m \mapsto_{a} \X{inl}\; \_} \ast
        \bigast{m \in [b, e)}{m \mapsto_{a} \_} \ast
        \; \tracefrag{t} \ast \pure{P(t)}
      \end{array}
    \end{array}
    \right\}
  \end{array}
  \end{array}
\]

@@

The resulting boot-code formulation of the robust safety theorem is now a
corollary of the general robust safety theorem, and has the following statement:
